parental migration and adolescents educational performance

### 2022-07-15 analysis/Gu-thesis-script.Rmd
reorganize file path

## Data cleaning
```{r Read data}
d_stu1 <- read_dta('cepsw1studentCN.dta') #wave 1 student
d_stu2 <- read_dta('cepsw2studentCN.dta') #wave 2 student
d_par1 <- read_dta('cepsw1parentCN.dta') #wave 1 parent
d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
```

>>>>

## Data cleaning
```{r Read data}
d_stu1 <- read_dta('cepsw1studentEN.dta') #wave 1 student
d_stu2 <- read_dta('cepsw2studentEN.dta') #wave 2 student
d_par1 <- read_dta('cepsw1parentEN.dta') #wave 1 parent
d_par2 <- read_dta('cepsw2parentEN.dta') #wave 2 parent
```
